\documentclass[12pt]{article}

\usepackage{amsmath, amsthm, amsfonts}

\title{Example article using \emph{WRITE -- with git}}
\author{Penelope Maher, \and Stephen Maher}

\usepackage[margin=4cm]{geometry} %change margin width

\usepackage{xspace}
\newcommand{\latex}{\LaTeX\xspace}

%preamble needed for WRITE - with git
\include{color_change}  

\usepackage{xcolor} 
\usepackage{xparse}
\usepackage[ddmmyy]{datetime}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\usepackage{setspace}
\setlength{\marginparwidth}{3.25cm}


\newcommand{\currentauthor}{Penny} %first name with capital to start.
\include{author_info}   

\newdate{rev1}{01}{01}{2017}
\date{\displaydate{rev1}}
\newdate{rev2}{09}{02}{2017}
\date{\displaydate{rev2}}

\newcommand{\rev}[1]{\displaydate{rev#1}}

\date{} %this just removes the date from the maketitle

\begin{document}

\maketitle

\abstract{Small example using \emph{WRITE -- with git} to write a journal article.}

\section{Introduction}

Writing a journal article in \latex has so many advantages over writing in an office product such as MS Word or libreoffice. But there are a few things \latex is missing. These include personalised track changes, personalised to-do notes and the ability to easily merge documents. So we wrote \emph{WRITE -- with git} to improve the writing experience in \latex. \Penny{\rev{1}}{Example to do note.}

The software that we have writted is a collection of shell scripts that utilise the diff managing ability of git. It simply compares all revisions of a document and produces a diff file that can be edited.


\section{Conclusions}
\Steve{\rev{2}}{Example with new date}

Using the package \emph{WRITE -- with git} you are able to create personalised `to do' notes that are dated and have a different colour for each author. After running the included scripts, a personalised diff file is created that conveniently displays all changes that have been made.

\end{document}
